A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-10 paper/paper.tex
Started addressing Patrick's comments

We assume that $G$ and $H$ are unlabelled, undirected graphs without loops
(Section~\ref{sec:extensions} describes how these restrictions may be relaxed).

@@

We use $n_G$ and $n_H$ to denote $|\V(G)|$ and $|\V(H)|$. We will occasionally use
and $n$ in complexity results to denote $n_G + n_H$.

@@

The most successful existing approaches to solving MCS are reformulation to the
maximum clique problem on one hand, and constraint programming
\cite{DBLP:conf/cp/McCreeshNPS16} on the other. In the clique encoding, an
association graph is created with one node for each pair in the set $\{(u,v)
\mid u \in \V(G), v \in \V(H) \}$ and an edge for each pair of mappings that
may be chosen together. A maximum clique in this graph corresponds directly to
a maximum common subgraph of $G$ and $H$.

In the constraint programming approach, we have a variable corresponding to
each vertex in $G$, and each variable initially has one value in its domain for
each vertex in $H$ to which it may be mapped, plus an additional value $\bot$
signifying that the vertex remains unmapped. A backtracking search is performed
in which values are assigned to variables, and propagation rules are used to
remove infeasible values from domains.

>>>>

We initially assume that $G$ and $H$ are unlabelled, undirected graphs without loops
(Section~\ref{sec:extensions} describes how these restrictions may be relaxed).

@@

We use $n_G$ and $n_H$ to denote $|\V(G)|$ and $|\V(H)|$. We will occasionally use
$n$ in complexity results to denote $n_G + n_H$.

@@

The most successful existing approaches to solving MCS are reformulation to the
maximum clique problem on one hand \cite{DBLP:conf/cp/McCreeshNPS16}, and
constraint programming on the other \cite{DBLP:conf/cp/NdiayeS11}. In the
clique encoding, an association graph is created with one node for each pair in
the set $\{(u,v) \mid u \in \V(G), v \in \V(H) \}$ and an edge for each pair of
mappings that may be chosen together. A maximum clique in this graph
corresponds directly to a maximum common subgraph of $G$ and $H$.

In the constraint programming approach, we have a variable corresponding to
each vertex in $G$, and each variable initially has one value in its domain for
each vertex in $H$ to which it may be mapped, plus an additional value $\bot$
signifying that the vertex remains unmapped. A backtracking search is performed
in which values are assigned to variables, and propagation rules are used to
remove infeasible values from domains.  A matching algorithm is used to propagate
a soft $\mathit{allDifferent}$ constraint. ? Say this better
